---
title: "visualization_ ggplot1"
author: "Jun"
date: "9/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggridges)
```

## create the weather data


```{r load_data, cache=TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## create a ggplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()

```

alternate way of making this plot

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

saving initial plots(mostly I don't use this)

```{r}
scatterplot = weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
scatterplot
```

adding color....

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4)
#alpha means transparency
```

why do `aes` positions matter?
first
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4)+geom_smooth(se = FALSE)
```

vs

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name))+ 
  geom_point(alpha = .4) + geom_smooth(se = FALSE)
```

facets

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(~ name)
```

this is fine, but not interesting

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha=.5) + 
  geom_smooth(size = 2, se = FALSE) +
  facet_grid(~name)
```
```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(tmax_fahr = tmax * (9 / 5) + 32,
         tmin_fahr = tmin * (9 / 5) + 32) %>% 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE)
```


## some extra stuff

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_smooth(size = 2, se = FALSE)
```

2d density

```{r}
#install.packages("hexbin")
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_hex() + facet_grid(~name)
```

## More kinds of plots

univariate plots
```{r}
weather_df %>% 
ggplot(aes(x = tmax, fill = name)) + 
  geom_histogram() +
  facet_grid(~name)
#color gives the outside lines around bars
#"dodge" rearrange the bar
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge", binwidth = 2)
```

density plot

```{r}
weather_df %>% 
ggplot(aes(x = tmax, fill = name)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")
```


univariate plot --- boxplots

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + geom_boxplot()
```


violin plots
(have density plot)
```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  stat_summary(fun.y = median, geom = "point", color = "blue", size = 4)
```

ridge plots!
useful for lots of groups
```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```


save image

```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
 geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)
```

```{r, fig.width=12}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha=.4) +
  geom_smooth(se = FALSE)

```


```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%")
```

```{r}
#ggplot(weather_df, aes(x = tmin, y = tmax)) + 
#  geom_point(aes(color = name))
```










